---
title: "Advanced R — Exercises"
author: "William Duke"
date: "10/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Foundations

##Names and values

###2.2.2 Exercises

1. The following code in fact binds the names a,b,c, and d to a vector of integers from 1:10.
```{r}
a <- 1:10
b <- a
c <- b
d <- 1:10
```

2. All reference functions find mean in the same place in memory.
```{r}
library(lobstr)
obj_addr(mean)
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
?make.names
```

3. Automatic conversion of non-syntactic names may not be the user's intention, if `read.csv` converts them without warning. This function can be turned off by setting `check.names` to `FALSE`.

4. `make.names` uses a series of rules to make names syntactic: The character "X" is prepended if necessary. All invalid characters are translated to ".". A missing value is translated to "NA". Names which match R keywords have a dot appended to them. Duplicated values are altered by make.unique.

5. 
4.

